Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-06 paper.tex
Add makefile, use file names from other projects for simplicity

For simplicity, we focus primarily on “non-complex” recombination nodes. To do
this, we apply a filtering step that removes those with more than one
breakpoint (and often more than two parent lineages), or where matching is not
HMM-consistent or identifies parents with different Pango lineage assignments
in the original (i.e., 5’ to 3’ end) and mirrored (i.e., 3’ to 5’ end) HMM
runs. Filtering reduces both the number of recombination nodes and breakpoints
from  A \& B to C in the wide ARG and from 726 & 806 to 459 in the long ARG
(Supplementary Tables 1 and 2). Note that in the unfiltered case, a single
recombination node can correspond to multiple points, one for each
recombination breakpoint. The effect of this filtering step in the long ARG,
which includes time periods of increased rates of coinfection and recombination
compared to the wide ARG, can be seen in Figure 3A (unfiltered) and Figure 3B
(filtered).

@@

\bibliographystyle{alpha}
\bibliography{references}

>>>>

For simplicity, we focus primarily on “non-complex” recombination nodes. To do
this, we apply a filtering step that removes those with more than one
breakpoint (and often more than two parent lineages), or where matching is not
HMM-consistent or identifies parents with different Pango lineage assignments
in the original (i.e., 5’ to 3’ end) and mirrored (i.e., 3’ to 5’ end) HMM
runs. Filtering reduces both the number of recombination nodes and breakpoints
from  A \& B to C in the wide ARG and from 726 \& 806 to 459 in the long ARG
(Supplementary Tables 1 and 2). Note that in the unfiltered case, a single
recombination node can correspond to multiple points, one for each
recombination breakpoint. The effect of this filtering step in the long ARG,
which includes time periods of increased rates of coinfection and recombination
compared to the wide ARG, can be seen in Figure 3A (unfiltered) and Figure 3B
(filtered).

@@

\bibliographystyle{alpha}
\bibliography{paper}
